### 2017-06-13 paper/paper.tex
Added the paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  My documentation report
%  Objetive: Explain what I did and how, so someone can continue with the investigation
%
% Important note:
% Chapter heading images should have a 2:1 width:height ratio,
% e.g. 920px width and 460px height.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,fleqn]{book} % Default font size and left-justified equations

\usepackage[top=3cm,bottom=3cm,left=3.2cm,right=3.2cm,headsep=10pt,letterpaper]{geometry} % Page margins

\usepackage{xcolor} % Required for specifying colors by name
\definecolor{ocre}{RGB}{52,177,201} % Define the orange color used for highlighting throughout the book

% Font Settings
\usepackage{avant} % Use the Avantgarde font for headings
%\usepackage{times} % Use the Times font for headings
\usepackage{mathptmx} % Use the Adobe Times Roman as the default text font together with math symbols from the Sym­bol, Chancery and Com­puter Modern fonts

\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage[utf8]{inputenc} % Required for including letters with accents
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs

% Bibliography
\usepackage[style=alphabetic,sorting=nyt,sortcites=true,autopunct=true,babel=hyphen,hyperref=true,abbreviate=false,backref=true,backend=biber]{biblatex}
\addbibresource{bibliography.bib} % BibTeX bibliography file
\defbibheading{bibempty}{}

\input{structure} % Insert the commands.tex file which contains the majority of the structure behind the template

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begingroup
\thispagestyle{empty}
\AddToShipoutPicture*{\put(0,0){\includegraphics[scale=1.25]{frontpage3}}} % Image background
\centering
\vspace*{5cm}
\par\normalfont\fontsize{32}{32}\sffamily\selectfont
\textbf{Filmchat}\\
{\LARGE Movie recommendation as NUI}\par % Book title
\vspace*{1cm}
{\Huge Tarjei Utnes}\par % Author name
\endgroup

%----------------------------------------------------------------------------------------
%	TABLE OF CONTENTS
%----------------------------------------------------------------------------------------

\chapterimage{head3.png} % Table of contents heading image

\pagestyle{empty} % No headers

\tableofcontents % Print the table of contents itself

%\cleardoublepage % Forces the first chapter to start on an odd page so it's on the right

\pagestyle{fancy} % Print headers again

%----------------------------------------------------------------------------------------
%	CHAPTER 1 Project Description
%----------------------------------------------------------------------------------------

\chapterimage{head3.png} % Chapter heading image

\chapter{Project Description}
This project is aimed for use at home, or possibly on-line in chat rooms or forums. The goal of the project is to interpret and come up with suggestions for which movies, or TV series its users should watch. I have limited the scope in this project to implement parts of the project, because of the available time given.
There are competing or projects existing that are close to doing what this project is aiming to do. Below is a non-exhaustive list of such projects, and solutions.
\section{“And Chill” Netflix recommendation bot}\index{AndChill}
The “And Chill” chatbot:
\begin{quote}
Well, that’s when the Facebook chatbot And Chill comes in handy. The bot asks you to suggest a film you like with a few reasons why, or to simply explain what you’re looking for in your next movie.  
Within a few moments, the bot should issue you with a short selection of trailers. It sometimes takes a while to compute, but it’s still a pretty efficient way of narrowing down Netflix’s massive library.
That said, if it’s running at peak capacity, you’ll have to wait your turn before it takes your requests. A representative for the app told a Facebook commenter last month that they were working on scaling capacity. (Huffington Post 2016)
\end{quote}
\section{Filmgrail}\index{Filmgrail}
Filmgrail is an app to check where you are able to watch the movie or television series you have selected. What makes Filmgrail unique in a Norwegian context, is that it covers many of the Norwegian streaming services. (Aftenposten, Filmgrail.com). At the moment, however 
\section{Google Assistant}\index{googleassistant}
Google Assistant can also recommend movies.

%----------------------------------------------------------------------------------------
%	CHAPTER 2 Interactive System Description
%----------------------------------------------------------------------------------------
\chapterimage{head3.png}

\chapter{Interactive System: Description}
There are two parts implemented in this system
The first part listens to a given channel on Slack, using the outgoing webhook (REFERENCE). 
The second part uses Googles Speech API (reference) and listens to the microphone. It then tries to search for the terms in the recognized speech and if it finds a movie within it it posts it to the same Slack channel.

The though of using both of these ways of integrating, was to be able to understand natural language surrounding how people talk and chat about movies, and then later on have the different parts use the same components.

%----------------------------------------------------------------------------------------
%	CHAPTER 3 Interactive System Design
%----------------------------------------------------------------------------------------

\chapterimage{head3.png}
\chapter{Interactive System: Design}
•	Sketches
•	Design rationale for the interface
•	Cost/benefit discussion of selected interaction techniques

Cost / Benefit of selected interaction techniques
Chat:
Chat is in my view has become a natural way of interacting, several times a day, I interact through chat, be it privately and also work related. A non-exhaustive list of some of the chat interaction I use during a day, or interactions close to chat, are:
- SMS or Textmessaging
- Microsoft Teams
- Slack
- Lync for Business (formerly Skype)
- Facebook Chat
- WhatsApp
- Snapchat 
- Tinder
- Happn
- Chat Support on company web pages
I would also claim that I am in no way unique using many different chat apps throughout the day, and would also therefore claim that chat has become a natural way of interacting with other people.

I would also claim that Chat has a low threshold, lower than using the phone, and it is more instant than using mail. As mail, is in a lot of ways an asynchronous way of communicating.

Speech Recognition:
I rarely use speech recognition, in other ways than as a "party trick". To me this is partly because of the social stigma talking to no one out and about, but the other important part is the lacking precision when I have tried it.

I would use the Speech Recognition in much the same way as I would use the

%----------------------------------------------------------------------------------------
%	CHAPTER 4 Interactive System: Development
%----------------------------------------------------------------------------------------

\chapterimage{head3.png}
\chapter{Interactive System: Development}
Description of how it was developed
o	If coding project, then include key code snippets and discuss them
o	If using a prototype tool, step-by-step description of how the interactive system was created

%----------------------------------------------------------------------------------------
%	CHAPTER 5 Interactive System: Evaluation
%----------------------------------------------------------------------------------------

\chapterimage{head3.png}
\chapter{Interactive System: Evaluation}
•	Evaluation plan for the interactive system incorporating at least 5 design principles from the course

%----------------------------------------------------------------------------------------
%	CHAPTER 6 Ten Meaningful Screens
%----------------------------------------------------------------------------------------

\chapterimage{head3.png}
\chapter{Ten Meaningful Screens}
List 10 meaningful screens that your interactive system provides and specify the operational sequence to find them.

%----------------------------------------------------------------------------------------
%	CHAPTER 7 Five Actionable Events
%----------------------------------------------------------------------------------------

\chapterimage{head3.png}
\chapter{Five Actionable Events}
List and discuss 5 actionable events encountered in your interactive system.

%----------------------------------------------------------------------------------------
%	CHAPTER 8 Two Valuable Outcomes
%----------------------------------------------------------------------------------------

\chapterimage{head3.png}
\chapter{Two Valuable Outcomes}
List and discuss two valuable organizational outcomes from using your interactive system: one in the short-term and the other in the long-term.

\vfill
%\textit{Wish you all the best, Andrea Hidalgo}
\end{document}

### 2017-06-13 paper/paper.tex
Updated paper

@@
 
-I would use the Speech Recognition in much the same way as I would use the
+In this project I have used the examples from Google, for their Google Speech API
+(REFERENCE)
+
+I have altered the code of the Recognize listener to post the results to a Web API running locally.
+
+But the actual recognized words, has been very limited, typically it has been limited to one, or two words, and not whole sentences.
+I have tried both using the laptops integrated microphone, but also a couple of different headsets. None of them have yielded very impressive results.
+Caveat: It could be that the actual implemtation example from Google is not the best one there is for my use case, and that improving on the recording part of it, and streaming data would be better.
+However, spending time working on this has not been a priority, so the actual implementation does nothing more than try to recognize a movie and then post the results about it to a channel on Slack.
 
@@
 \chapter{Interactive System: Development}
+I chose to start with an implementation of Speech Recognition, as this was the initial idea of the project.
+Some quick googling, and I landed on Googles Speech API (REFERENCE). There is an online tester (LINK)
+
+First I had to enable the Speech API in the Google Cloud console. The API is limited to a certain amount of seconds in the free tier.
+
+First I tried using the Node JS library, but I was not able to get the sound recorder to work properly on my Windows 10 laptop. (It might work better on a linux or Mac, but I am not sure of that)
+
+I then moved on to C# as I am somewhat familiar with that language. The speech recorder part of that worked much better, and I was able to get the example code to recognize my speech quite quickly.
+After I got it working, I modified the code to post the recognized speech to the designated Slack channel.
+
+I selected Slack, as I have developed a couple of things for posting to its interface earlier, and the familiarty meant I was able to test and implement the speech recognition quicker, than had I selected Facebook Messenger API, or Microsofts similar products.
+The selection here was then based on familiarity and not based on necessarily "Best of breed" for my specific task.
+
+Next part of the development was the "omdbsearcher".
+Here I selected OMDB (Open Movie Database) and had to donate a couple of dollars to get access to their API.
+There are implementations for IMDB, but they are not, to my knowledge authorized by IMDB, and I was not interested in spending time on a non official api.
+
+IMDB Also has some of its data dumped to a FTP on regular intervals, so creating an own database could have been a future work part for this project.
+
+The omdbsearcher I implemented in Node JS, as this is the language I can program in fastest.
+I tested a couple of request with Postman (reference) which is a tool to create web requests to different endpoints.
+Postman also has a nice feature where you can get the code for replicating the request in different languages.
+
+I then created a local webserver serving the incoming recognized speech, and then trying to search for them on OMDB. If it got a hit, it posted it to the Slack Channel I had selected.
+
 Description of how it was developed
@@
 •	Evaluation plan for the interactive system incorporating at least 5 design principles from the course
+Unfortunately, even though the TextBlob (reference) python Library is good, it is still lacking with regards to the goal of my project.
+It is able to, sometimes recognize the noun phrase and sentiment, but it is not always the case.
+Also keeping context of a ongoing discussion is not something I have looked into at all.
+However, I do not think this will not be possible to solve in the future, however they might be "hard" problems.
+
+The speech recognition part of the project, albeit fun, did not fulfill my hopes for what it was able to do.
+For me to be able to do that, I would probably have to work some time on the actual recording of the audio, and how to optimize this part.
+Also having the audio recorder being able to switch on and off based on speech patterns.
+Also recognizing who actually speaks, is not something I have seen covered in the documentation.
+For recognizing users, a chatroom with identified users, is easier.
 
@@
 \vfill
-%\textit{Wish you all the best, Andrea Hidalgo}
 \end{document}

### 2017-06-14 paper/paper.tex
Updated paper

@@
 \chapter{Project Description}
+I am starting with the vision for this project. Imagine the following scenario.
+You, and one or more friends, or maybe a romantic partner, are sitting int the sofa.
+You are having a movie night, but you are not quite sure what you should see.
+While you sit and discuss your likes, and dislikes, there is a microphone hidden in the corner.
+The listens to what you are saying, and it is sending it to an Interactive System.
+It understands, who is speaking, who is liking a movie, and who is not liking a movie.
+It also has, from earlier experience knowledge of what you and maybe the ones you are with have seen, and liked.
+It also knows what you did not like.
+
+After a few minutes discussing with the people it starts rolling some suggestions over the television.
+
+By using your voice, you can tell the Interactive system to play a trailer, if it is showing you something you think might be interesting.
+
+When you have decided it knows on what streaming, or maybe even traditional linear TV the movie plays on and selects that option for you.
+
+The name of the system, is Filmchat.
+
 This project is aimed for use at home, or possibly on-line in chat rooms or forums.
@@
 
-I then moved on to C# as I am somewhat familiar with that language. The speech recorder part of that worked much better, and I was able to get the example code to recognize my speech quite quickly.
+I then moved on to C\# as I am somewhat familiar with that language. The speech recorder part of that worked much better, and I was able to get the example code to recognize my speech quite quickly.
 After I got it working, I modified the code to post the recognized speech to the designated Slack channel.
@@
 
+Generally speaking I would say that, unfortunately my interactive system does not provide that valuable of outcomes.
+However here I will try to describe the two, that I thought came the closest.
+
+1:
+Speech recognition of movies. Being able to search for, and find ratings for movies without having to use the telephone, could be something I might use.
+
+Especially if there was a way of starting to play the movie automatically, once I was happy with the selection.
+
+However for a home theater version of this to work, the description and possibly the ability to play a trailer would have to be done on the Television, and maybe not in a Slack channel.
+
+2:
+Being able to detect how people talk about movies, and then recommending them movies based on what they might also like i think could be very valuable.
+
+The difficulty of course would be the level of Natural Language Processing to make this as seamless as I would want it to be.
+
+My rather simple implementation of using a Python library to detect noun phrases, and sentiment values, can work on some of the sentences people can say, and write about movies, but it does not keep context.
+
+For both of these outcomes I would, however say, that for me it has been valuable to learn, and try to make the mostly "off-the-shelf" technology work together to create these solutions.
+And with the amount of time available I am rather happy with what I was able to create.
+
+Future work in this might be interesting, and I do believe that better time, and better knowledge of the API's libraries etcetera would mean a better performing Interactive System.
+
 \vfill

### 2017-06-14 paper/paper.tex
Updated paper

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{Filmchat}
 
@@
 % Bibliography
-\usepackage[style=alphabetic,sorting=nyt,sortcites=true,autopunct=true,babel=hyphen,hyperref=true,abbreviate=false,backref=true,backend=biber]{biblatex}
-\addbibresource{bibliography.bib} % BibTeX bibliography file
+%\usepackage[style=alphabetic,sorting=nyt,sortcites=true,autopunct=true,babel=hyphen,hyperref=true,abbreviate=false,backref=true,backend=biber]{biblatex}
+
+%\defbibheading{bibempty}{}
+
+\usepackage[style=ieee,sorting=nyt,sortcites=true,autopunct=true,babel=hyphen,hyperref=true,abbreviate=false,backref=true,backend=biber]{biblatex}
+\addbibresource{Mendeley_MA-230.bib} % BibTeX bibliography file
 \defbibheading{bibempty}{}
@@
 \chapter{Project Description}
-I am starting with the vision for this project. Imagine the following scenario.
-You, and one or more friends, or maybe a romantic partner, are sitting int the sofa.
+I am starting with the vision for this project.
+
+Imagine the following scenario.You, and one or more friends, or maybe a romantic partner, are sitting int the sofa in front of the TV.
 You are having a movie night, but you are not quite sure what you should see.
@@
 It understands, who is speaking, who is liking a movie, and who is not liking a movie.
-It also has, from earlier experience knowledge of what you and maybe the ones you are with have seen, and liked.
+It also has, from earlier experience, knowledge of what you and maybe the ones you are with have seen, and liked.
 It also knows what you did not like.
@@
 The name of the system, is Filmchat.
+
+The goal of the system; To help you decide on the best movie for you, and your friends to watch right now.
+
+\cite{WigdorBraveWorld}
 
@@
 That said, if it’s running at peak capacity, you’ll have to wait your turn before it takes your requests.
-A representative for the app told a Facebook commenter last month that they were working on scaling capacity.
-(Huffington Post 2016)
+A representative for the app told a Facebook commenter last month that they were working on scaling capacity.\cite{Williams2016TheUK}
 \end{quote}
@@
 What makes Filmgrail unique in a Norwegian context, is that it covers many of the Norwegian streaming services.
-(Aftenposten, Filmgrail.com).
+\cite{AmundsenAppenAftenposten}.
 At the moment, however
@@
 Google Assistant can also recommend movies.
+
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{google_assitant.png}
+  \caption{Usage of payment instrument millions of transactions (in Norway) 2001 to 2014\cite{Bank2014NoregsKunderetta}}
+  \label{fig:use_of_payment_instrument}
+\end{figure}
 
@@
 There are two parts implemented in this system
-The first part listens to a given channel on Slack, using the outgoing webhook (REFERENCE). 
-The second part uses Googles Speech API (reference) and listens to the microphone.
+The first part listens to a given channel on Slack, using the outgoing webhook.
+\cite{SlackOutgoingSlack}
+The second part uses Googles Speech API \cite{GoogleCloudPlatformSpeechPlatform} and listens to the microphone.
 It then tries to search for the terms in the recognized speech and if it finds a movie within it it posts it to the same Slack channel.

### 2017-06-14 paper/paper.tex
Updated python code, to correct format

@@
 \chapter{Project Description}
-I am starting with the vision for this project.
-
+\section{Vision}
 Imagine the following scenario.You, and one or more friends, or maybe a romantic partner, are sitting int the sofa in front of the TV.
@@
 
-\cite{WigdorBraveWorld}
-
 This project is aimed for use at home, or possibly on-line in chat rooms or forums.
@@
 There are competing or projects existing that are close to doing what this project is aiming to do. Below is a non-exhaustive list of such projects, and solutions.
-\section{“And Chill” Netflix recommendation bot}\index{AndChill}
+\section{Competing and nearby Interactive Systems}\index{competing systems}
+While the list is by no means an exhaustive one, these are some of the known interactive systems doing things near to what I want my system to do. None of them has the complete solution.
+\subsection{“And Chill” Netflix recommendation bot}\index{AndChill}
 The “And Chill” chatbot:
@@
 \end{quote}
-\section{Filmgrail}\index{Filmgrail}
+While the And Chill bot, has a nice, based on my experience, recommendation system it is still the task of having to actually sit and chat to a bot.
+This, to me feels unnecessarily tedious, and somewhat unnatural.
+However the recommendation engine that sits behind the bot I think is very good.
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{and_chill_bot.png}
+  \caption{And Chill recommending a movie}
+  \label{fig:and_chill}
+\end{figure}
+
+\subsection{Filmgrail}\index{Filmgrail}
 Filmgrail is an app to check where you are able to watch the movie or television series you have selected.
@@
 \cite{AmundsenAppenAftenposten}.
-At the moment, however
-\section{Google Assistant}\index{googleassistant}
+At the moment, however, it does not have a "recommendation" engine.
+It has some "Popular searches" and other similar things, but nothing that can recommend based on what you have watched, or what you like.
+This could change in the future.
+\subsection{Google Assistant}\index{googleassistant}
 Google Assistant can also recommend movies.
+See Fig \ref{fig:google_assistant}.
+It uses my geographical location, or context to recommend a movie that I am able to watch on the cinema nearby.
+In the example shown in Fig \ref{fig:google_assistant} I was using speech recognition to have it recommend the movie.
+
+The recommendations I have gotten from the Google Assistan has not been very exciting, and to me atleast, not very relevant.
+The speech recognition however, is very good.
+Better than the one I was able to implement using Googles Speech API.
 
@@
   \centering
-   \includegraphics[width=0.77\textwidth]{google_assitant.png}
-  \caption{Usage of payment instrument millions of transactions (in Norway) 2001 to 2014\cite{Bank2014NoregsKunderetta}}
-  \label{fig:use_of_payment_instrument}
+   \includegraphics[width=0.77\textwidth]{google_assistant.png}
+  \caption{Google Assitant recommending a movie based on geographic context}
+  \label{fig:google_assistant}
 \end{figure}
@@
 
-The though of using both of these ways of integrating, was to be able to understand natural language surrounding how people talk and chat about movies, and then later on have the different parts use the same components.
+The thought of using both of these ways of integrating, was to be able to understand natural language surrounding how people talk and chat about movies, and then later on have the different parts use the same components.
 
+The vision of the project, not the actual implementation sadly, aimed to follow the design guidelines give in the chapter about Social Natural User Interfaces \(NUI\) that Wigdor and Wixon talks about in ther Brave NUI World book.
+\cite{WigdorBraveWorld}
+
+Some of the ones I believe fitting to Filmchat are:
+\begin{itemize}
+\item Create an experience that comes alive with several users, so that the experience
+is more fun or efficient when many hands are working simultaneously
+\item Enable new users to join, so that the approval of additional users allows them
+to easily engage with your application, without disrupting other users already
+present.
+\item Be able to continue with fewer users, allowing one user to leave without disrupting all others’ experience.
+\end{itemize}
+I believe them fitting because in the social context of watching a movie the, the experience would come alive, when people are sitting and discussing their likes, and dislikes.
+This could, of course be the case in a chat-room setting such as Slack, as well.
 %----------------------------------------------------------------------------------------
@@
 \chapter{Interactive System: Design}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{system_flow.png}
+  \caption{System Flow for Filmchat}
+  \label{fig:system_flow}
+\end{figure}
 •	Sketches
@@
 
-Cost / Benefit of selected interaction techniques
-Chat:
+\section{Cost / Benefit of selected interaction techniques}
+\subsection{Chat}
 Chat is in my view has become a natural way of interacting, several times a day, I interact through chat, be it privately and also work related.
 A non-exhaustive list of some of the chat interaction I use during a day, or interactions close to chat, are:
-- SMS or Textmessaging
-- Microsoft Teams
-- Slack
-- Lync for Business (formerly Skype)
-- Facebook Chat
-- WhatsApp
-- Snapchat 
-- Tinder
-- Happn
-- Chat Support on company web pages
+\begin{itemize}
+\item SMS or Textmessaging
+\item Microsoft Teams
+\item Slack
+\item Lync for Business (formerly Skype)
+\item Facebook Chat
+\item WhatsApp
+\item Snapchat 
+\item Tinder
+\item Happn
+\item Chat Support on company web pages
+\end{itemize}
+
 I would also claim that I am in no way unique using many different chat apps throughout the day, and would also therefore claim that chat has become a natural way of interacting with other people.
@@
 
-Speech Recognition:
+\subsection{Speech Recognition}
 I rarely use speech recognition, in other ways than as a "party trick".
@@
 In this project I have used the examples from Google, for their Google Speech API
-(REFERENCE)
-
+\cite{GoogleCloudPlatformSpeechPlatform}
 I have altered the code of the Recognize listener to post the results to a Web API running locally.
@@
 \chapter{Ten Meaningful Screens}
-List 10 meaningful screens that your interactive system provides and specify the operational sequence to find them.
+\section{Speech recognition}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{speech_recognition_c-sharp.PNG}
+  \caption{Speech recognition using the CSharp SDK for Google Speech}
+  \label{fig:c-sharp-speech}
+\end{figure}
+To get to this screen Fig\ref{fig:c-sharp-speech}, you have to compile the C\# project located under speech-recognizer folder in the GitHub project. \cite{Github2017GitHubProject}
+Then you would have to enable the Speech API in the Google Cloud Console, and then finally compile the C\# and run it.
+When you are able to execute the program, you type in "Recognize.exe listen".
+The program will then, using the microphone it detects on your system.
+Listen for audio and send this to the Speech API for recognition.
+It will then return them to the cli, and also post them to the Omdbsearcher.
+
+\newpage
+\section{Using the Omdbsearcher}
+The omdbsearcher Fig\ref{fig:omdbsearcher} part of Filmchat is located under the Omdsearcher folder in the GitHub project \cite{Github2017GitHubProject}.
+It is based on NodeJS, so first step is to install the neccessary packages by doing: \"npm install\".
+Then you start it by executing the command: \"node index.js\".
+This will in turn start a small webserver running on port 3000.
+It listens for JSON-formatted data.
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{omdbsearcher.PNG}
+  \caption{Omdbsearcher in the cli}
+  \label{fig:omdbsearcher}
+\end{figure}
+For debugging purposes it outputs the search results from the JSON POST it got.
+
+\newpage
+\section{Posting to the Omdbsearcher}
+For developing purposes, it is possible to post directly to the Omdbsearcher without using the other components. See Fig\ref{fig:postman-film}
+
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{postman_sending_film_title.PNG}
+  \caption{Postman sending film title}
+  \label{fig:postman-film}
+\end{figure}
+
+\newpage
+\section{Result in Slack}
+When either posting with Postman, or using the speech recognition component, the results looks like this in the designated Slack channel. Fig\ref{fig:slack-result}
+
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{slack_result.PNG}
+  \caption{Result from post to Omdbsearcher in Slack}
+  \label{fig:slack-result}
+\end{figure}
+
+\newpage
+\section{Sending sentences to TextBlob}
+To start the TextBlob Botlistener, go to the textblob folder in the GitHub project \cite{Github2017GitHubProject}.
+Install the libararies \"pip install libraries\" and run \"python bot-listener.py\" this will start a webservice running on port 8080, that listens for sentences posted to it.
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{textblob_botlistener.PNG}
+  \caption{TextBlob Python library webservice}
+  \label{fig:slack-result}
+\end{figure}
+
+\newpage
+\section{Sending sentences to TextBlob part 2}
+To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
+  \caption{Sending a sentence to TextBlob Botlistener}
+  \label{fig:sending-botlistener}
+\end{figure}
+
+\newpage
+\section{Combining the TextBlob Botlistener and the Omdbsearcher}
+To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
+  \caption{Sending a sentence to TextBlob Botlistener}
+  \label{fig:sending-botlistener}
+\end{figure}
+
+\section{Combining the TextBlob Botlistener and the Omdbsearcher}
+To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
+  \caption{Sending a sentence to TextBlob Botlistener}
+  \label{fig:sending-botlistener}
+\end{figure}
+
+\section{Combining the TextBlob Botlistener and the Omdbsearcher}
+To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
+  \caption{Sending a sentence to TextBlob Botlistener}
+  \label{fig:sending-botlistener}
+\end{figure}
+
+\section{Combining the TextBlob Botlistener and the Omdbsearcher}
+To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
+  \caption{Sending a sentence to TextBlob Botlistener}
+  \label{fig:sending-botlistener}
+\end{figure}
+
+\section{Combining the TextBlob Botlistener and the Omdbsearcher}
+To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
+  \caption{Sending a sentence to TextBlob Botlistener}
+  \label{fig:sending-botlistener}
+\end{figure}
 
@@
 \chapter{Five Actionable Events}
-List and discuss 5 actionable events encountered in your interactive system.
+I was not able to find that many actionable events in my Interactive System, but the ones I did find I cover in this section.
+\section{}
 
@@
 \chapter{Two Valuable Outcomes}
-List and discuss two valuable organizational outcomes from using your interactive system: one in the short-term and the other in the long-term.
-
 Generally speaking I would say that, unfortunately my interactive system does not provide that valuable of outcomes.
@@
 
-1:
+\section{Speech recognition of movies}
 Speech recognition of movies. Being able to search for, and find ratings for movies without having to use the telephone, could be something I might use.
-
+I also thik that this could be a short term valuable outcome of the system.
 Especially if there was a way of starting to play the movie automatically, once I was happy with the selection.
-
 However for a home theater version of this to work, the description and possibly the ability to play a trailer would have to be done on the Television, and maybe not in a Slack channel.
 
-2:
-Being able to detect how people talk about movies, and then recommending them movies based on what they might also like i think could be very valuable.
-
-The difficulty of course would be the level of Natural Language Processing to make this as seamless as I would want it to be.
-
-My rather simple implementation of using a Python library to detect noun phrases, and sentiment values, can work on some of the sentences people can say, and write about movies, but it does not keep context.
-
+\section{Detect how people talk about movies}
+On the longer term I would say that being able to detect how people talk about movies, and then recommending them movies based on what they might also like i think could be very valuable.
+The difficulty of course would be the level of Natural Language Processing\cite{Wikipedia2017NaturalProcessing} to make this as seamless as I would want it to be.
+My rather simple implementation of using a Python library \cite{TextBlobTutorial:Documentation} to detect noun phrases, and sentiment values, can work on some of the sentences people can say, and write about movies, but it does not keep context.
+\section{Summary of outcomes}
 For both of these outcomes I would, however say, that for me it has been valuable to learn, and try to make the mostly "off-the-shelf" technology work together to create these solutions.
@@
 
+\printbibliography
+
 \vfill

### 2017-06-14 textblob/bot-listener.py

@@ -10,7 +10,6 @@ users = {}
 import http.client
 def findMovieTitle(input):
     conn = http.client.HTTPConnection("localhost:3000")
-
     #payload = "{\"text\":\"Gone with the wind\"}"
     payload = "{\"text\":\"" + input + "\"}"
     #payload = {"text": "Gone with the wind"}
@@ -36,26 +35,32 @@ def findMovieTitle(input):
 
 @app.route('/api/', methods=['POST'])
 def api_post():
-    text = request.json['text']
-    username = request.json['user_name']
-
-    testimonial = TextBlob(text)
-    sent = testimonial.sentiment.polarity
-    print (testimonial.noun_phrases)
-    if (len(testimonial.noun_phrases) > 0):
-        noun = testimonial.noun_phrases[0]
+    #text = request.json['text']
+    text = request.form['text']
+    #username = request.json['user_name']
+    username = request.form['user_name']
+    if (username == "slackbot"):
+        return jsonify("OK")
     else:
-        noun = "Did not find movie"
+        testimonial = TextBlob(text)
+        sent = testimonial.sentiment.polarity
+        print (testimonial.noun_phrases)
+        if (len(testimonial.noun_phrases) > 0):
+            noun = testimonial.noun_phrases[0]
+        else:
+            noun = "Did not find movie"
+       
+        
+        findMovieTitle(noun)
+        if (username in users):
+            users[username][noun] = sent
+        else:
+            users[username] = {noun: sent}
+        print (users) #Debug
+        
+        return jsonify(text = username + " has a sentiment value " + str(sent) + " for " + noun)
     
-    
-    findMovieTitle(noun)
-    if (username in users):
-        users[username][noun] = sent
-    else:
-        users[username] = {noun: sent}
-    print (users) #Debug
-    #return "OK"
-    return jsonify(text = username + " has a sentiment value " + str(sent) + " for " + noun)
+        
 
 
 @app.route('/api/', methods=['GET'])

### 2017-06-14 paper/paper.tex
Updated paper again

@@
 \end{figure}
-
+\newpage
+\section{Combining the TextBlob Botlistener and the Omdbsearcher}
+To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
+  \caption{Sending a sentence to TextBlob Botlistener}
+  \label{fig:sending-botlistener}
+\end{figure}
+\newpage
 \section{Combining the TextBlob Botlistener and the Omdbsearcher}
@@
 
-\section{Combining the TextBlob Botlistener and the Omdbsearcher}
-To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\newpage
+\section{Everything together, almost}
+Here \(Fig\ref{fig:everything-together}\), almost all the components are playing together.
+I write a chat message in the designated Slack channel, while running both the Omdbsearcher, and the TextBlob botlistener, and the result, along with the sentiment gets posted to the channel.
+The only part, not here, is the Speech Recognizer, as I was not able to make it recognize more than a word, here and there.
+
 \begin{figure}[]
   \centering
-   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
-  \caption{Sending a sentence to TextBlob Botlistener}
-  \label{fig:sending-botlistener}
-\end{figure}
-
-\section{Combining the TextBlob Botlistener and the Omdbsearcher}
-To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
-\begin{figure}[]
-  \centering
-   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
-  \caption{Sending a sentence to TextBlob Botlistener}
-  \label{fig:sending-botlistener}
+   \includegraphics[width=0.77\textwidth]{everything_together.PNG}
+  \caption{Everything together}
+  \label{fig:everything-together}
 \end{figure}

### 2017-06-14 paper/paper.tex
Updated paper again

@@
 \chapter{Interactive System: Development}
+\section{Overarching Goal}
+The main goal for me, was to see what was possible to do, using mostly "off the shelf" components, being libraries, API's or other available premade solutions.
+This because the project had a limited time, and I wanted to be as effective as possible.
+\section{Speech recognition}
 I chose to start with an implementation of Speech Recognition, as this was the initial idea of the project.
-Some quick googling, and I landed on Googles Speech API (REFERENCE). There is an online tester (LINK)
+Some quick googling, and I landed on Google's Speech API \cite{GoogleCloudPlatformSpeechPlatform}. There is an on-line tester, where you can talk, and the Web Page will print what you say.
 
@@
 
+\section{Omdbsearcher}
 Next part of the development was the "omdbsearcher".
@@
 
-IMDB Also has some of its data dumped to a FTP on regular intervals, so creating an own database could have been a future work part for this project.
+IMDB Also has some of its data dumped to a FTP on regular intervals, so creating an own database could have been a future work part for this project. \cite{IMDbAlternativeInterfaces}
 
-The omdbsearcher I implemented in Node JS, as this is the language I can program in fastest.
-I tested a couple of request with Postman (reference) which is a tool to create web requests to different endpoints.
+The Omdbsearcher I implemented in Node JS, as this is the language I can program in fastest.
+I tested a couple of request with Postman, which is a tool to create web requests to different endpoints.
 Postman also has a nice feature where you can get the code for replicating the request in different languages.
@@
 
+\section{Textblob Botlistener}
+I then checked out a couple of different ways of intepreting language, but have from other projects, already knowledge that Python has such libraries that are good, and with good performance.
+I therefore winded up with TextBlob, which is a library that can both get sentiment, and noun phrases\cite{WikipediaNounPhrase} from sentences.
+\cite{TextBlobTutorial:Documentation}
+I therefore just had to create a webservice interface for the TextBlob, and was able to do this quickly.
+
 Description of how it was developed
@@
 o	If using a prototype tool, step-by-step description of how the interactive system was created
+
+\section{Spelling corrector}
+While the Textblob Botlistener was able to get the noun phrase\cite{WikipediaNounPhrase} of sentences about movie, and that this sometimes is an actual movie, this is not always the case.
+Therefore I thought about using some autocorrect or spelling corrections, but using the freely available IMDB datasets as valid words \cite{IMDbAlternativeInterfaces}.
+I found a good example by Peter Norvig \cite{NorvigHowCorrector} on how to do it.
+But both the development, and the performance was rather slow, and the dataset would have needed quite a lot of cleaning before I could have used it.
+Therefore I decided on not to implement this part, and to put it off to a possible future work.
 

### 2017-06-15 paper/paper.tex
Updated paper

@@
 \section{Vision}
-Imagine the following scenario.You, and one or more friends, or maybe a romantic partner, are sitting int the sofa in front of the TV.
+Imagine the following scenario.You, and one or more friends, or maybe a romantic partner, are sitting in the sofa in front of the TV.
 You are having a movie night, but you are not quite sure what you should see.
@@
 \chapter{Interactive System: Description}
-There are two parts implemented in this system
-The first part listens to a given channel on Slack, using the outgoing webhook.
-\cite{SlackOutgoingSlack}
-The second part uses Googles Speech API \cite{GoogleCloudPlatformSpeechPlatform} and listens to the microphone.
+There are three parts implemented in this system
+The first part listens to a given channel on Slack, using the outgoing web hook\cite{SlackOutgoingSlack}.This is the TextBlob Botlisener.Then there is the component that listens to a post message and tries to find a movie from that message.
+This is the Omdbsearcher.
+The third part is the Speech Regognizer which is heavily based on the Csharp example from Googles Speech API \cite{GoogleCloudPlatformSpeechPlatform} and listens to the microphone.
 It then tries to search for the terms in the recognized speech and if it finds a movie within it it posts it to the same Slack channel.
 
+\section{TextBlob Botlistener}
+A Python web service that uses Textblob\cite{TextBlobTutorial:Documentation} as a way of getting noun phrase, and sentiment from the text it is provided.
+It gets input from the designated slack channel, using the outgoing web hook \cite{SlackOutgoingSlack}.
+The TextBlob Botlistener listens to port 8080 by default.
+
+\section{Speech Recognizer}
+The Speech recognizer, is based on the Google Speech API \cite{GoogleCloudPlatformSpeechPlatform} and is programmed in Csharp.
+The code is mostly just adapted to post to a web interface, in addition to printing to the console / cli.
+The Speech Recognizer listens to the detected microphone on the computer by default.
+It keeps a python dictionary of the users, and their, movie and their most recent sentiment score in memory.
+
+\section{Omdbsearcher}
+The Omdbsearcher is based on the Open Movie Data base API.\cite{OMDbDatabase}.
+When it gets text it will try to search for this text on the OMDB Api and return the JSON formatted result if it finds something, or return a negative result if it does not find anything.
+The web service listens to port 3000 by default.
+
+\newpage
+\section{Architecture}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{system_flow.png}
+  \caption{System Flow for Filmchat}
+  \label{fig:system_flow}
+\end{figure}
 The thought of using both of these ways of integrating, was to be able to understand natural language surrounding how people talk and chat about movies, and then later on have the different parts use the same components.
+This is also why I opted for a modular approach building small components, that I could add to on a later point, and that was easy to test using Postman.
 
-The vision of the project, not the actual implementation sadly, aimed to follow the design guidelines give in the chapter about Social Natural User Interfaces \(NUI\) that Wigdor and Wixon talks about in ther Brave NUI World book.
+\section{Description of the vision}
+The vision of the project, not the actual implementation sadly, aimed to follow the design guidelines give in the chapter about Social Natural User Interfaces \(NUI\) that Wigdor and Wixon talks about in their Brave NUI World book.
 \cite{WigdorBraveWorld}
@@
 This could, of course be the case in a chat-room setting such as Slack, as well.
+In Fig\ref{fig:system_flow} the modular approach can be seen, and building more components, or hooking into third party API's could easily be done.
 %----------------------------------------------------------------------------------------
@@
 \chapter{Interactive System: Design}
-\begin{figure}[]
-  \centering
-   \includegraphics[width=0.77\textwidth]{system_flow.png}
-  \caption{System Flow for Filmchat}
-  \label{fig:system_flow}
-\end{figure}
-•	Sketches
-•	Design rationale for the interface
-•	Cost/benefit discussion of selected interaction techniques
+\section{System Flow}
+The system has three main user inputs \(see Fig\ref{fig:system_flow}\) of which two of them are implemented.
+They are the Speech recognition, and the Chat.
+The Chat in the implementation listens to a Slack channel using the outgoing web hook \cite{SlackOutgoingSlack}.
+It then forwards to the sentiment analysis to extract sentiment and noun phrase \cite{WikipediaNounPhrase} this could have been forwarded to other more advanced third party Natural Language Processors\cite{Wikipedia2017NaturalProcessing} such as Wit.AI\cite{Wit.aiWit.ai} and API.AI\cite{API.AIConversationalAPI.AI}.
+But I decided to use a light weight Python based for faster development, and easier debugging.
+
+The last input, would have used the same modules, but would have gotten their input from a chat room.
+The difference would have been the more asynchronous behavior of that kind of interaction, but sentiments and information could have been harvested in much the same way.
+\section{Design rationale}
 

### 2017-06-15 omdbsearcher/index.js
Updated and cleaned up some of the sources

@@ -31,7 +31,6 @@ app.post("/", function(req, res) {
 			if (error) throw new Error(error);
 			postToSlack(JSON.parse(body), options.qs.t)
 			res.send("OK");
-			//console.log(body);
 		});
 
 	} else {
@@ -50,7 +49,6 @@ function postToSlack(result, searchterm) {
 		slackMessage = "Movie with searchterm: " + searchterm + " not found!";
 	} else {
 		slackMessage = formatResult(result);
-		//slackMessage = formatResult(result);
 	}
 	var slackOptions = {
 		method: 'POST',

### 2017-06-15 textblob/bot-listener.py

@@ -49,8 +49,6 @@ def api_post():
             noun = testimonial.noun_phrases[0]
         else:
             noun = "Did not find movie"
-       
-        
         findMovieTitle(noun)
         if (username in users):
             users[username][noun] = sent

### 2017-06-15 paper/paper.tex
Updates

@@
 
-The recommendations I have gotten from the Google Assistan has not been very exciting, and to me atleast, not very relevant.
+The recommendations I have gotten from the Google Assistant has not been very exciting, and to me at least, not very relevant.
 The speech recognition however, is very good.
-Better than the one I was able to implement using Googles Speech API.
+Better than the one I was able to implement using Google's Speech API.
 
@@
 This is the Omdbsearcher.
-The third part is the Speech Regognizer which is heavily based on the Csharp example from Googles Speech API \cite{GoogleCloudPlatformSpeechPlatform} and listens to the microphone.
+The third part is the Speech Recognizer which is heavily based on the C sharp example from Google's Speech API \cite{GoogleCloudPlatformSpeechPlatform} and listens to the microphone.
 It then tries to search for the terms in the recognized speech and if it finds a movie within it it posts it to the same Slack channel.
@@
 \section{TextBlob Botlistener}
-A Python web service that uses Textblob\cite{TextBlobTutorial:Documentation} as a way of getting noun phrase, and sentiment from the text it is provided.
+A Python web service that uses TextBlob\cite{TextBlobTutorial:Documentation} as a way of getting noun phrase, and sentiment from the text it is provided.
 It gets input from the designated slack channel, using the outgoing web hook \cite{SlackOutgoingSlack}.
@@
 \section{Design rationale}
+In the Brave NUI World\cite{Wigdor2010BraveWorld} Wigdor and Wilson leads by saying the following about Natural User interfaces and their design guidelines:
+\begin{itemize}
+\item Create an experience that, for expert users, can feel like an extension of their body.
+\item Create an experience that feels just as natural to a novice as it does to an
+expert user.
+\item Create an experience that is authentic to the medium—do not start by trying to
+mimic the real world or anything else.
+\item Build a user interface that considers context, including the right metaphors,
+visual indications, feedback, and input/output methods for the context.
+\item Avoid falling into the trap of copying existing user interface paradigms.
+\end{itemize}
+
+The emphasis on creating an experience that feels natural, both for the novice, and for the expert, is why I chose to use Speech recognition and chat.
+During the day I do both chat and speak quite a lot, and if there was a way of enhancing all this interaction to my benefit I would welcome it, and feel it was both natural and seamless.
+This is why I wanted it to be able to listen to conversations both written and spoken.
 
@@
 I would also claim that I am in no way unique using many different chat apps throughout the day, and would also therefore claim that chat has become a natural way of interacting with other people.
-
-I would also claim that Chat has a low threshold, lower than using the phone, and it is more instant than using mail. As mail, is in a lot of ways an asynchronous way of communicating.
+I would also claim that Chat has a low threshold, lower even, than using the phone, and it is more instant than using mail. As mail, is in a lot of ways an asynchronous way of communicating.
 
@@
 I rarely use speech recognition, in other ways than as a "party trick".
-To me this is partly because of the social stigma talking to no one out and about, but the other important part is the lacking precision when I have tried it.
+To me this is partly because of the social stigma talking to no one out in social settings, but the other important part is the lacking precision when I have tried it.
 
@@
 I have tried both using the laptops integrated microphone, but also a couple of different headsets. None of them have yielded very impressive results.
-Caveat: It could be that the actual implemtation example from Google is not the best one there is for my use case, and that improving on the recording part of it, and streaming data would be better.
+Caveat: It could be that the actual implementation example from Google is not the best one there is for my use case, and that improving on the recording part of it, and streaming data would be better.
 However, spending time working on this has not been a priority, so the actual implementation does nothing more than try to recognize a movie and then post the results about it to a channel on Slack.
+\subsection{Privacy}
+I would also raise the issue of the feeling, real or not about privacy and having something listen into your conversations as I have envisioned here.
+I think that people might be reluctant to have a device or app listen in on them in their own home, without them having full control of who could listen in.
 
@@
 %----------------------------------------------------------------------------------------
-
 \chapterimage{head3.png}
@@
 The main goal for me, was to see what was possible to do, using mostly "off the shelf" components, being libraries, API's or other available premade solutions.
-This because the project had a limited time, and I wanted to be as effective as possible.
+This because the project had a limited time, and I wanted to be as effective as possible with my time.
 \section{Speech recognition}
@@
 I then moved on to C\# as I am somewhat familiar with that language. The speech recorder part of that worked much better, and I was able to get the example code to recognize my speech quite quickly.
-After I got it working, I modified the code to post the recognized speech to the designated Slack channel.
+After I got it working, I modified the code to post the recognized speech to the designated Slack channel. I then modified it to post to the Omdbsearcher. 
+\newpage
+The code as be seen below the "Post to SLACK" comment are the lines I had to add to make this work.
+\begin{verbatim}
+foreach (var alternative in result.Alternatives)
+  {
+    Console.WriteLine(alternative.Transcript);
+    // Post to SLACK
+    var client = new RestClient("http://localhost:3000/");
+    var request = new RestRequest(Method.POST);
+    request.AddHeader("content-type", "application/json");
+    request.AddHeader("accept", "application/json");
+    request.AddParameter("application/json", "{\"text\":\"" + alternative.Transcript + "\"}"
+    , ParameterType.RequestBody);
+    IRestResponse response = client.Execute(request);
+}
+\end{verbatim}
 
-I selected Slack, as I have developed a couple of things for posting to its interface earlier, and the familiarty meant I was able to test and implement the speech recognition quicker, than had I selected Facebook Messenger API, or Microsofts similar products.
+I selected Slack, as I have developed a couple of things for posting to its interface earlier, and the familiarity meant I was able to test and implement the speech recognition quicker, than had I selected Facebook Messenger API, or Microsofts similar products.
 The selection here was then based on familiarity and not based on necessarily "Best of breed" for my specific task.
@@
 \section{Omdbsearcher}
-Next part of the development was the "omdbsearcher".
-Here I selected OMDB (Open Movie Database) and had to donate a couple of dollars to get access to their API.
-There are implementations for IMDB, but they are not, to my knowledge authorized by IMDB, and I was not interested in spending time on a non official api.
+Next part of the development was the Omdbsearcher.
+Here I selected OMDB (Open Movie Database)\cite{OMDbDatabase} and had to donate a couple of dollars to get access to their API.
+There are "hacks" and implementations for IMDB, but they are not, to my knowledge authorized by IMDB, and I was not interested in spending time on a non official API.
 
@@
 
-I then created a local webserver serving the incoming recognized speech, and then trying to search for them on OMDB. If it got a hit, it posted it to the Slack Channel I had selected.
+I then created a local web server serving the incoming recognized speech, and then trying to search for them on OMDB. If it got a hit, it posted it to the Slack Channel I had selected.
+\newpage
+\subsection{Omdbsearcher listener route}
+\begin{verbatim}
+app.post("/", function(req, res) {
+    if (req.body.text) {
+      console.log("Searching for on OMDB: " + req.body.text)
+        options.qs.t = req.body.text;
+        request(options, function(error, response, body) {
+            if (error) throw new Error(error);
+            postToSlack(JSON.parse(body), options.qs.t)
+            res.send("OK");
+        });
+     } else {
+     res.send("Got no input");
+    }
+});
+\end{verbatim}
+This listener route listens to a HTTP POST JSON with "text" key. It then searches for the text in OMDB. Either way it posts to the Slackchannel using the postToSlack function.
+\newpage
+\subsection{Omdbsearcher post to slack}
+\begin{verbatim}
+function postToSlack(result, searchterm) {
+    var slackMessage;
+    if (result.Response != "True") {
+        console.log(result);
+        slackMessage = "Movie with searchterm: " + searchterm + " not found!";
+      } else {
+        slackMessage = formatResult(result);
+    }
+    var slackOptions = {
+        method: 'POST',
+        url: config.slackurl,
+        headers: {
+            'cache-control': 'no-cache',
+            'content-type': 'application/json',
+            accept: 'application/json'
+        },
+        body: slackMessage,
+        json: true
+    };
+    request(slackOptions, function(error, response, body) {
+        if (error) throw new Error(error);
+        console.log(body);
+    });
+}
+\end{verbatim}
+This function posts the formatted result to Slack. To be able to do this you have to generate the key which is hardcoded into the "config.slackurl" string.
 
 \section{Textblob Botlistener}
-I then checked out a couple of different ways of intepreting language, but have from other projects, already knowledge that Python has such libraries that are good, and with good performance.
+I then checked out a couple of different ways of interpreting language.
+Among them I looked at Wit.AI\cite{Wit.aiWit.ai}, and also looked at API.AI\cite{API.AIConversationalAPI.AI}.
+While both of them looked promising, the scope of this project meant I should probably use something simpler and faster to implement.
+From other projects, I already have the knowledge that Python has such libraries that are both good, and with good performance.
 I therefore winded up with TextBlob, which is a library that can both get sentiment, and noun phrases\cite{WikipediaNounPhrase} from sentences.
 \cite{TextBlobTutorial:Documentation}
-I therefore just had to create a webservice interface for the TextBlob, and was able to do this quickly.
-
-Description of how it was developed
-o If coding project, then include key code snippets and discuss them
-o If using a prototype tool, step-by-step description of how the interactive system was created
+I therefore just had to create a web service interface for the TextBlob, and was able to do this quickly.
+\newpage
+\begin{verbatim}
+@app.route('/api/', methods=['POST'])
+def api_post():
+    #text = request.json['text']
+    text = request.form['text']
+    #username = request.json['user_name']
+    username = request.form['user_name']
+    if (username == "slackbot"):
+        return jsonify("OK")
+    else:
+        testimonial = TextBlob(text)
+        sent = testimonial.sentiment.polarity
+        print (testimonial.noun_phrases)
+        if (len(testimonial.noun_phrases) > 0):
+            noun = testimonial.noun_phrases[0]
+        else:
+            noun = "Did not find movie"
+        findMovieTitle(noun)
+        if (username in users):
+            users[username][noun] = sent
+        else:
+            users[username] = {noun: sent}
+        print (users) #Debug
+        return jsonify(text = username + " has a sentiment value " + str(sent) + " for " + noun)
+\end{verbatim}
+This code snippet listens to the route "/api/" it gets the text and user name formatted as application/x-www-form-urlencoded and then using the TextBlob library extracts the sentiment\cite{WikipediaSentimentAnalysis} and noun phrase\cite{WikipediaNounPhrase}.
 
 \section{Spelling corrector}
-While the Textblob Botlistener was able to get the noun phrase\cite{WikipediaNounPhrase} of sentences about movie, and that this sometimes is an actual movie, this is not always the case.
-Therefore I thought about using some autocorrect or spelling corrections, but using the freely available IMDB datasets as valid words \cite{IMDbAlternativeInterfaces}.
+While the Textblob Botlistener was able to get the noun phrase\cite{WikipediaNounPhrase} of sentences about movies, and that this sometimes is an actual movie, it is not always the case.
+Therefore I thought about using some auto-correct or spelling corrections, but using the freely available IMDB datasets as valid words \cite{IMDbAlternativeInterfaces}.
 I found a good example by Peter Norvig \cite{NorvigHowCorrector} on how to do it.
@@
 Therefore I decided on not to implement this part, and to put it off to a possible future work.
+The beginning work can be seen in the Github\cite{Github2017GitHubProject} under the did-you-mean folder.
 
@@
 \chapter{Interactive System: Evaluation}
-• Evaluation plan for the interactive system incorporating at least 5 design principles from the course
-Unfortunately, even though the TextBlob (reference) python Library is good, it is still lacking with regards to the goal of my project.
+In this part I have used the design guidelines from chapter 2 given in the book Brave NUI\cite{Wigdor2010BraveWorld} world to evaluate my project.
+
+"[the] goal is to build a user experience
+that is natural to your user, rather than somehow intrinsically natural\cite{Wigdor2010BraveWorld}."
+
+\section{Create an experience that, for expert users, can feel like an extension of their
+body}
+The voice recognition, had it been better, and not so sensitive to the quality of the microphone could have felt like an extension of the users body.
+Most people speak naturally to other people many times a day.
+The actual implementation unfortunately is neither natural nor very good.
+
+\section{Create an experience that feels just as natural to a novice as it does to an
+expert user}
+I would argue that both the chat and the speech recognition are both interfaces that are natural to both the novice and the expert.
+I have mentioned earlier in this project report that I use chat many times a day, and that this is in no part unique to me.
+I therefore think that this part lives up to the design guideline in a good way.
+
+\section{Create an experience that is authentic to the medium, do not start by trying to
+mimic the real world or anything else}
+Evaluating the Chat part of the interaction I would claim that this is indeed very true to the medium.
+Users are able to chat, and their sentiments surrounding movies are recorded.
+I could easily turn of that it posts to the channel every time someone mentions a movie, and instead use the in-memory sentiment database of the TextBlob bot listener only when there was a need to look at it.
+
+\section{Build a user interface that considers context, including the right metaphors,
+visual indications, feedback, and input/output methods for the context}
+I also believe, that by being true to the chat medium I am able to keep the input output, metaphors and indications as they are expected to be according to the mental models of that medium.
+
+\section{Avoid falling into the trap of copying existing user interface paradigms}
+I think I might be guilty of copying existing paradigms, in that I have gotten inspiration from other existing solutions.
+Be they "And Chill"\cite{Williams2016TheUK} or other chatbots and recommendation engines.
+
+\section{General evaluation}
+Unfortunately, even though the TextBlob\cite{TextBlobTutorial:Documentation} Python Library is good, it is still lacking with regards to the goal of my project.
 It is able to, sometimes recognize the noun phrase and sentiment, but it is not always the case.
 Also keeping context of a ongoing discussion is not something I have looked into at all.
-However, I do not think this will not be possible to solve in the future, however they might be "hard" problems.
+However, I do think this will be possible to solve in the future.
+Even though this might be "hard" problems.
 
@@
 Also recognizing who actually speaks, is not something I have seen covered in the documentation.
-For recognizing users, a chatroom with identified users, is easier.
+For recognizing users, a chat room with identified users, is easier, this is also the most promising for future work in the short term.
 
@@
 \newpage
+\section{First posts from the speech recognizer to Slack}
+Here we can see the different alternatives the Speech API suggest and that get posted to Slack. See Fig\ref{fig:first-posts}
+
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{first_posts.PNG}
+  \caption{First speech recognized}
+  \label{fig:first-posts}
+\end{figure}
+
+\newpage
 \section{Posting to the Omdbsearcher}
@@
 \section{Sending sentences to TextBlob}
-To start the TextBlob Botlistener, go to the textblob folder in the GitHub project \cite{Github2017GitHubProject}.
-Install the libararies \"pip install libraries\" and run \"python bot-listener.py\" this will start a webservice running on port 8080, that listens for sentences posted to it.
+To start the TextBlob Botlistener, go to the TextBlob folder in the GitHub project \cite{Github2017GitHubProject}.
+Install the libraries \"pip install libraries\" and run \"python bot-listener.py\" this will start a web service running on port 8080, that listens for sentences posted to it.
 \begin{figure}[]
@@
    \includegraphics[width=0.77\textwidth]{textblob_botlistener.PNG}
-  \caption{TextBlob Python library webservice}
+  \caption{TextBlob Python library web service}
   \label{fig:slack-result}
@@
 
-\section{Combining the TextBlob Botlistener and the Omdbsearcher}
-To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
+\newpage
+\section{Getting the status from the TextBlob Botlistener}
+To get the current status of the users and their sentiments around movies, a simple GET to the /api/ will return a JSON formatted result as seen in Fig\ref{fig:sending-botlistener} Negative values are negative sentiments, and as closer the value gets to 1, the better the sentiment.
 \begin{figure}[]
   \centering
-   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
-  \caption{Sending a sentence to TextBlob Botlistener}
-  \label{fig:sending-botlistener}
-\end{figure}
-\newpage
-\section{Combining the TextBlob Botlistener and the Omdbsearcher}
-To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
-\begin{figure}[]
-  \centering
-   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
-  \caption{Sending a sentence to TextBlob Botlistener}
-  \label{fig:sending-botlistener}
-\end{figure}
-\newpage
-\section{Combining the TextBlob Botlistener and the Omdbsearcher}
-To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
-\begin{figure}[]
-  \centering
-   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
-  \caption{Sending a sentence to TextBlob Botlistener}
-  \label{fig:sending-botlistener}
+   \includegraphics[width=0.77\textwidth]{get_textblob.PNG}
+  \caption{Getting status of sentiments}
+  \label{fig:sentiment-status}
 \end{figure}
@@
 \chapterimage{head3.png}
-\chapter{Five Actionable Events}
-I was not able to find that many actionable events in my Interactive System, but the ones I did find I cover in this section.
-\section{}
+\chapter{Actionable Events}
+I have here, deemed it necessary to limit the number of actionable events to two. This is because I only have two actionable events in the implementation I have created.
+\section{User says the name of a movie}
+When a user says the name of the movie, and the Speech Recognizer is running, it will post the results it was able to find in the designated Slack channel.
+
+\section{User writes a sentiment about a movie}
+If a user writes a sentiment about a movie, the components will try to search for that movie, and post the result, if it can find one, and the sentiment that user has given about it.
 
@@
 
-Future work in this might be interesting, and I do believe that better time, and better knowledge of the API's libraries etcetera would mean a better performing Interactive System.
+Future work in this might be interesting, and I do believe that better time, and better knowledge of the API's libraries would mean a better performing Interactive System.
 
@@
 
-\vfill
+%\vfill
 \end{document}

### 2017-06-15 textblob/bot-listener.py

@@ -31,7 +31,13 @@ def findMovieTitle(input):
 #    r = requests.post('http://localhost:3000/', data = jsonify({'text':input}))
 #    print(r.content())
     
-
+def formatUsers(input):
+    message = ""
+    for user in input:
+        message = "\n" + message + user + " "
+        for movie in input[user]:
+            message = message + " " + movie + " score:"+ str(input[user][movie])
+    return message
 
 @app.route('/api/', methods=['POST'])
 def api_post():
@@ -55,12 +61,15 @@ def api_post():
         else:
             users[username] = {noun: sent}
         print (users) #Debug
-        
         return jsonify(text = username + " has a sentiment value " + str(sent) + " for " + noun)
     
-        
+@app.route('/status/', methods=['POST'])
+def api_status():
+    status = formatUsers(users)
+    return jsonify({"text": status})
 
 
+#Gets the current in-memory status of users, movies and sentiments
 @app.route('/api/', methods=['GET'])
 def api_get():
     return jsonify(users)

### 2017-06-15 paper/paper.tex
Updates updates updates

@@
    \includegraphics[width=0.77\textwidth]{google_assistant.png}
-  \caption{Google Assitant recommending a movie based on geographic context}
+  \caption{Google Assistant recommending a movie based on geographic context}
   \label{fig:google_assistant}
@@
 \section{Speech Recognizer}
-The Speech recognizer, is based on the Google Speech API \cite{GoogleCloudPlatformSpeechPlatform} and is programmed in Csharp.
+The Speech recognizer, is based on the Google Speech API \cite{GoogleCloudPlatformSpeechPlatform} and is programmed in C sharp.
 The code is mostly just adapted to post to a web interface, in addition to printing to the console / cli.
@@
 The Omdbsearcher is based on the Open Movie Data base API.\cite{OMDbDatabase}.
-When it gets text it will try to search for this text on the OMDB Api and return the JSON formatted result if it finds something, or return a negative result if it does not find anything.
+When it gets text it will try to search for this text on the OMDB API and return the JSON formatted result if it finds something, or return a negative result if it does not find anything.
 The web service listens to port 3000 by default.
@@
 expert user.
-\item Create an experience that is authentic to the medium—do not start by trying to
+\item Create an experience that is authentic to the medium, do not start by trying to
 mimic the real world or anything else.
@@
 \begin{itemize}
-\item SMS or Textmessaging
+\item SMS or Text messaging
 \item Microsoft Teams
@@
 
-First I tried using the Node JS library, but I was not able to get the sound recorder to work properly on my Windows 10 laptop. (It might work better on a linux or Mac, but I am not sure of that)
+First I tried using the Node JS library, but I was not able to get the sound recorder to work properly on my Windows 10 laptop. (It might work better on a Linux or Mac, but I am not sure of that)
 
@@
 \end{verbatim}
-This function posts the formatted result to Slack. To be able to do this you have to generate the key which is hardcoded into the "config.slackurl" string.
+This function posts the formatted result to Slack. To be able to do this you have to generate the key which is hard coded into the "config.slackurl" string.
 
-\section{Textblob Botlistener}
+\section{TextBlob Botlistener}
 I then checked out a couple of different ways of interpreting language.
@@
 \section{Spelling corrector}
-While the Textblob Botlistener was able to get the noun phrase\cite{WikipediaNounPhrase} of sentences about movies, and that this sometimes is an actual movie, it is not always the case.
+While the TextBlob Botlistener was able to get the noun phrase\cite{WikipediaNounPhrase} of sentences about movies, and that this sometimes is an actual movie, it is not always the case.
 Therefore I thought about using some auto-correct or spelling corrections, but using the freely available IMDB datasets as valid words \cite{IMDbAlternativeInterfaces}.
@@
 Therefore I decided on not to implement this part, and to put it off to a possible future work.
-The beginning work can be seen in the Github\cite{Github2017GitHubProject} under the did-you-mean folder.
+The beginning work can be seen in the GitHub\cite{Github2017GitHubProject} under the did-you-mean folder.
 
@@
    \includegraphics[width=0.77\textwidth]{speech_recognition_c-sharp.PNG}
-  \caption{Speech recognition using the CSharp SDK for Google Speech}
+  \caption{Speech recognition using the C Sharp SDK for Google Speech}
   \label{fig:c-sharp-speech}
@@
 \section{Using the Omdbsearcher}
-The omdbsearcher Fig\ref{fig:omdbsearcher} part of Filmchat is located under the Omdsearcher folder in the GitHub project \cite{Github2017GitHubProject}.
-It is based on NodeJS, so first step is to install the neccessary packages by doing: \"npm install\".
+The Omdbsearcher Fig\ref{fig:omdbsearcher} part of Filmchat is located under the Omdbsearcher folder in the GitHub project \cite{Github2017GitHubProject}.
+It is based on NodeJS, so first step is to install the necessary packages by doing: \"npm install\".
 Then you start it by executing the command: \"node index.js\".
-This will in turn start a small webserver running on port 3000.
+This will in turn start a small web server running on port 3000.
 It listens for JSON-formatted data.
@@
 To get the current status of the users and their sentiments around movies, a simple GET to the /api/ will return a JSON formatted result as seen in Fig\ref{fig:sending-botlistener} Negative values are negative sentiments, and as closer the value gets to 1, the better the sentiment.
+There is also the possibility of using a /sentiment command in the designated Slack channel.
+See Fig\ref{fig:sentiment-command}
 \begin{figure}[]
@@
 \end{figure}
+\begin{figure}[]
+  \centering
+   \includegraphics[width=0.77\textwidth]{sentiments_command.PNG}
+  \caption{Sentiment command}
+  \label{fig:sentiment-command}
+\end{figure}
 
@@
 Here \(Fig\ref{fig:everything-together}\), almost all the components are playing together.
-I write a chat message in the designated Slack channel, while running both the Omdbsearcher, and the TextBlob botlistener, and the result, along with the sentiment gets posted to the channel.
+I write a chat message in the designated Slack channel, while running both the Omdbsearcher, and the TextBlob Botlistener, and the result, along with the sentiment gets posted to the channel.
 The only part, not here, is the Speech Recognizer, as I was not able to make it recognize more than a word, here and there.
@@
 
+\section{User can access the status of the sentiments}
+If a user in the Slack channel wants to check the current status of the sentiments, he or she can write /sentiments, and he will get the currents status from the TextBlob Botlistener.
+
 %----------------------------------------------------------------------------------------
@@
 Generally speaking I would say that, unfortunately my interactive system does not provide that valuable of outcomes.
-However here I will try to describe the two, that I thought came the closest.
+However here I will try to describe the three, that I thought came the closest.
 
@@
 Speech recognition of movies. Being able to search for, and find ratings for movies without having to use the telephone, could be something I might use.
-I also thik that this could be a short term valuable outcome of the system.
+I also think that this could be a short term valuable outcome of the system.
 Especially if there was a way of starting to play the movie automatically, once I was happy with the selection.

### 2017-06-15 paper/paper.tex
final commit

@@
 Imagine the following scenario.You, and one or more friends, or maybe a romantic partner, are sitting in the sofa in front of the TV.
-You are having a movie night, but you are not quite sure what you should see.
-While you sit and discuss your likes, and dislikes, there is a microphone hidden in the corner.
+You are having a movie night, but you are not quite sure what you should watch.
+While you sit and discuss your likes and dislikes, there is a microphone hidden in the corner.
 The listens to what you are saying, and it is sending it to an Interactive System.
@@
 
-When you have decided it knows on what streaming, or maybe even traditional linear TV the movie plays on and selects that option for you.
+When you have decided, it knows on what streaming service, or maybe even traditional linear TV the movie plays and selects that option for you.
 
@@
 
-The goal of the system; To help you decide on the best movie for you, and your friends to watch right now.
+The goal of the system; to help you decide on the best movie for you, and your friends to watch right now.
 
@@
 \section{TextBlob Botlistener}
-A Python web service that uses TextBlob\cite{TextBlobTutorial:Documentation} as a way of getting noun phrase, and sentiment from the text it is provided.
+A Python web service that uses TextBlob\cite{TextBlobTutorial:Documentation} as a way of getting noun phrase\cite{WikipediaNounPhrase}, and sentiment\cite{WikipediaSentimentAnalysis} from the text it is provided.
 It gets input from the designated slack channel, using the outgoing web hook \cite{SlackOutgoingSlack}.
+It is programmed in Python.
+It keeps a python dictionary of the users, and their, movie and their most recent sentiment score in memory.
 The TextBlob Botlistener listens to port 8080 by default.
@@
 The Speech Recognizer listens to the detected microphone on the computer by default.
-It keeps a python dictionary of the users, and their, movie and their most recent sentiment score in memory.
 
@@
 When it gets text it will try to search for this text on the OMDB API and return the JSON formatted result if it finds something, or return a negative result if it does not find anything.
+Omdbsearcher is programmed in NodeJS.
 The web service listens to port 3000 by default.
@@
 \end{figure}
-The thought of using both of these ways of integrating, was to be able to understand natural language surrounding how people talk and chat about movies, and then later on have the different parts use the same components.
+The idea behind using both chat and voice as interfaces, was to be able to understand natural language surrounding in the context of how people talk and chat about movies.
+Then later on have the different parts use the same components.
 This is also why I opted for a modular approach building small components, that I could add to on a later point, and that was easy to test using Postman.
@@
 \subsection{Speech Recognition}
-I rarely use speech recognition, in other ways than as a "party trick".
+I rarely use speech recognition in other ways than as a "party trick".
 To me this is partly because of the social stigma talking to no one out in social settings, but the other important part is the lacking precision when I have tried it.
@@
 \newpage
-\section{Combining the TextBlob Botlistener and the Omdbsearcher}
-To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
-\begin{figure}[]
-  \centering
-   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
-  \caption{Sending a sentence to TextBlob Botlistener}
-  \label{fig:sending-botlistener}
-\end{figure}
-
-\newpage
 \section{Getting the status from the TextBlob Botlistener}
 To get the current status of the users and their sentiments around movies, a simple GET to the /api/ will return a JSON formatted result as seen in Fig\ref{fig:sending-botlistener} Negative values are negative sentiments, and as closer the value gets to 1, the better the sentiment.
-There is also the possibility of using a /sentiment command in the designated Slack channel.
-See Fig\ref{fig:sentiment-command}
 \begin{figure}[]
@@
 \end{figure}
+
+\newpage
+\section{Getting the status in the Slack channel}
 \begin{figure}[]
@@
 \end{figure}
+There is also the possibility of using a /sentiment command in the designated Slack channel to get the same status as in the previous section. See Fig\ref{fig:sentiment-command}
 
@@
 Here \(Fig\ref{fig:everything-together}\), almost all the components are playing together.
-I write a chat message in the designated Slack channel, while running both the Omdbsearcher, and the TextBlob Botlistener, and the result, along with the sentiment gets posted to the channel.
+I write a chat message in the designated Slack channel, while running both the Omdbsearcher, and the TextBlob otlistener, and the result, along with the sentiment gets posted to the channel.
 The only part, not here, is the Speech Recognizer, as I was not able to make it recognize more than a word, here and there.
